The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-04 paper.tex
update

  \begin{figure}
    \includegraphics[width=1.0\linewidth]{figures/fig__initial-density-profile.png}
    \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
    \label{fig__initial-density-profile}
  \end{figure}

  \begin{figure}
      \includegraphics[width=1.0\linewidth]{figures/fig__numberDensityHistogram.png}
      \caption{The initial density distribution of the number density\
               for a settling ISM without jet source.} % caption
      \label{fig__numberDensityHistogram}
  \end{figure}

@@

@@

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The profile of $\rho_{\text{isoDisk}}(z)$ along z-axis.}
    \label{fig__initial-density-profile}
  \end{figure}

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
      \caption{The initial density distribution of the number density\
               for a settling ISM without jet source.} % caption
      \label{fig__numberDensityHistogram}
  \end{figure}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
    \caption{The slice of pressure (top), temperature (middle), and number density (bottom)\
             in the y-z plane passing through the center of the disk.}
    \label{fig__zoom-in-disk}
  \end{figure}

@@

  \begin{figure*}
    \includegraphics[width=\linewidth]{figures/fig__xRay.png}
    \caption{One-dimensional surface-brightness\
             profiles in the same energy band\
             , cut at various galactic latitudes (as labelled).\
             For comparison, we also show ...}
    \label{fig__xRay.png}
  \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__gammaRay.png}
  \caption{The simulated photon flux at  2 GeV (top), 10 GeV (middle), and 100 GeV (bottom).}
  \label{fig__gammaRay}
\end{figure*}
